A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-02-06 paper.tex
Creates "submission.tar.gz", which is the right .tar.gz file for submission to arxiv

{\centering \includegraphics[width=0.75\linewidth]{/Users/ntie0001/github/njtierney/ddd/figures/directory-structure}

@@

{\centering \includegraphics[width=0.75\linewidth]{/Users/ntie0001/github/njtierney/ddd/figures/json-code}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{/Users/ntie0001/github/njtierney/ddd/figures/data_sharing_workflow} \caption{The steps required compared to effort required for data sharing for reproducibility.}\label{fig:data-sharing-workflow}
\end{figure}

@@

{\centering \includegraphics[width=0.6\linewidth]{/Users/ntie0001/github/njtierney/ddd/figures/sdss-raw-data-screenshot}

>>>>

{\centering \includegraphics[width=0.75\linewidth]{figures/directory-structure}

@@

{\centering \includegraphics[width=0.75\linewidth]{figures/json-code}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{figures/data_sharing_workflow} \caption{The steps required compared to effort required for data sharing for reproducibility.}\label{fig:data-sharing-workflow}
\end{figure}

@@

{\centering \includegraphics[width=0.6\linewidth]{figures/sdss-raw-data-screenshot}
